% \sectionTitle{Career-Best Publications (See full list \href{https://sites.google.com/view/tamdblp/publications}{here})}{\faBook}
\sectionTitle{Publications}{\faBook}

\begin{pub}
\normalsize
\pubentry{}{{\textbf{\color{blue} Journal Articles}}}
\pubentry{Sci. China Inf. Sci. 2025 (IF~7.6, Q1)}{
Minh Hieu Nguyen, Thanh Trung Huynh, Thanh Toan Nguyen, Phi Le Nguyen, Hien Thu Pham, Jun Jo, Thanh Tam Nguyen.
\textbf{On-device diagnostic recommendation with heterogeneous federated BlockNets}.
In Science China Information Sciences 2025.
}

\pubentry{Sci. Rep. 2022 (IF~3.9, Q1)}{
Anh Duy Nguyen, Phi Le Nguyen, Viet Hung Vu, Quoc Viet Pham, Viet Huy Nguyen, Minh Hieu Nguyen, Thanh Hung Nguyen, Kien Nguyen.
\textbf{Accurate discharge and water level forecasting using ensemble learning with genetic algorithm and singular spectrum analysis-based denoising}.
In Scientific Reports 2022.
}

\pubentry{KBS 2022 (IF~7.6, Q1)}{
Thanh Tam Nguyen, Thanh Cong Phan, Minh Hieu Nguyen, Matthias Weidlich, Hongzhi Yin, Jun Jo, Quoc Viet Hung Nguyen.
\textbf{Model-agnostic and diverse explanations for streaming rumour graphs}.
In Knowledge-Based Systems 2022.
}

\pubentry{ACM TOSN 2022 (IF~4.1, Q2)}{
La Van Quan, Minh Hieu Nguyen, Thanh Hung Nguyen, Kien Nguyen, Phi Le Nguyen.
\textbf{On the global maximization of network lifetime in wireless rechargeable sensor networks}.
In ACM Transactions on Sensor Networks 2022.
}

\pubentry{IEEE Access 2021 (IF~3.367, Q1)}{
Minh Hieu Nguyen, Phi Le Nguyen, Kien Nguyen, Van An Le, Thanh Hung Nguyen, Yusheng Ji.
\textbf{PM2.5 prediction using genetic algorithm-based feature selection and encoder-decoder model}.
In IEEE Access 2021.
}
\normalsize

%\bigskip
\pubentry{}{}
\pubentry{}{{\textbf{\color{blue} Conference Papers}}}
\pubentry{ICDE 2025 (CORE~A*)}{
Minh Hieu Nguyen, Viet Hung Doan, Anh Tuan Nguyen, Jun Jo, Quoc Viet Hung Nguyen.
\textbf{Streaming counterfactual subset selection with bias awareness}.
In International Conference on Data Engineering (ICDE) 2025.
}

\pubentry{ECML-PKDD 2024 (CORE~A)}{
Dong Duc Anh Nguyen, Minh Hieu Nguyen, Phi Le Nguyen, Jun Jo, Hongzhi Yin, Thanh Tam Nguyen.
\textbf{Multi-task learning of heterogeneous hypergraph representations in LBSNs}.
In Advanced Data Mining and Applications (ADMA) 2024.
}

\pubentry{ADMA 2024 (CORE~B)}{
Dong Duc Anh Nguyen, Minh Hieu Nguyen, Phi Le Nguyen, Jun Jo, Hongzhi Yin, Thanh Tam Nguyen.
\textbf{Multi-task learning of heterogeneous hypergraph representations in LBSNs}.
In Advanced Data Mining and Applications 2024.
}

\pubentry{ADC 2024 (CORE~B)}{
Hien Thu Pham, Minh Hieu Nguyen, Hiep Minh Ha, Ngoc Quang Hung Le, Jun Jo.
\textbf{Towards comprehensive innovation landscape: Technology retrieval meets large language models}.
In Australasian Database Conference 2024.
}

\pubentry{WSDM 2023 (CORE~A*)}{
Thanh Trung Huynh, Minh Hieu Nguyen, Thanh Tam Nguyen, Phi Le Nguyen, Matthias Weidlich, Quoc Viet Hung Nguyen, Karl Aberer.
\textbf{Efficient integration of multi-order dynamics and internal dynamics in stock movement prediction}.
In WSDM 2023.
}

\pubentry{ACIIDS 2022 (CORE~B)}{
Minh Hieu Nguyen, Viet Huy Nguyen, Thanh Trung Huynh, Thanh Hung Nguyen, Quoc Viet Hung Nguyen, Phi Le Nguyen.
\textbf{A lightweight and efficient GA-based model-agnostic feature selection scheme for time series forecasting}.
In ACIIDS 2022.
}

\pubentry{ACIIDS 2022 (CORE~B)}{
Minh Tam Pham, Thanh Dat Hoang, Minh Hieu Nguyen, Viet Hung Vu, Thanh Trung Huynh, Quyet Thang Huynh.
\textbf{Social multi-role discovering with hypergraph embedding for location-based social networks}.
In ACIIDS 2022.
}

\pubentry{IEA/AIE 2021 (CORE~B)}{
Anh Duy Nguyen, Viet Hung Vu, Minh Hieu Nguyen, Duc Viet Hoang, Thanh Hung Nguyen, Kien Nguyen, Phi Le Nguyen.
\textbf{Efficient prediction of discharge and water levels using ensemble learning and singular-spectrum analysis-based denoising}.
In IEA/AIE 2021.
}


\end{pub}