\sectionTitle{Career-Best Publications (See full list \href{https://sites.google.com/view/tamdblp/publications}{here})}{\faBook}

\begin{pub}
\normalsize
\pubentry{}{{\textbf{\color{blue} Journal Articles}}}

%\small
\pubentry{CSUR 2024 (Top 2\%, IF 16.6, $A^*$)}{Thanh Toan Nguyen, Quoc Viet Hung Nguyen, Thanh Tam Nguyen, Thanh Trung Huynh, Thanh Thi Nguyen, Matthias Weidlich, Hongzhi Yin. \textbf{Manipulating Recommender Systems: A Survey of Poisoning Attacks and Countermeasures}. In ACM Computing Surveys 2024.}
\pubentry{KBS 2024 ($Q1$, IF 8.8)}{Thanh Tam Nguyen, Zhao Ren, Thanh Toan Nguyen, Jun Jo, Quoc Viet Hung Nguyen, Hongzhi Yin. \textbf{Portable graph-based rumour detection against multi-modal heterophily}. In Knowledge-based Systems 2024.}
\pubentry{IEEE-CIM 2024 (Top 10\%, IF 9.0)}{ Zhao Ren, Yi Chang, Thanh Tam Nguyen, Yang Tan, Kun Qian, Björn W. Schuller. \textbf{A Comprehensive Survey on Heart Sound Analysis in the Deep Learning Era}. In IEEE Computational Intelligence Magazine 2024.}
\pubentry{Inf. Sci 2023 (Top 10\%, IF 8.233)}{ Thanh Tam Nguyen, Thanh Cong Phan, Minh Hieu Nguyen, Thanh Thi Nguyen, Jun Jo, Quoc Viet Hung Nguyen. \textbf{Example-based Explanations for Streaming Fraud Detection on Graphs}. In Information Sciences 2023.}
\pubentry{KBS 2023 ($Q1$, IF 8.8)}{Thanh Tam Nguyen, Thanh Trung Huynh, Minh Tam Pham, Thanh Thi Nguyen, Hongzhi Yin, Quoc Viet Hung Nguyen. \textbf{Validating Functional Redundancy with Mixed Generative Adversarial Networks}. In Knowledge-based Systems 2023.}
\pubentry{JBHI 2023 ($Q1$, $A^*$)}{ Zhao Ren, Björn W. Schuller, Björn M. Eskofier, Thanh Tam Nguyen, Wolfgang Nejdl. \textbf{Guest Editorial Trustworthy and Collaborative AI for Personalised Healthcare through Edge-of-Things}. In Journal of Biomedical and Health Informatics 2023.}
\pubentry{JVLDB 2022 ($A^*$)}{ Nguyen Thanh Tam, Matthias Weidlich, Nguyen Quoc Viet Hung. \textbf{Detecting Rumors with Latency Guarantees using Massive Data Stream}. In JVLDB 2022.}
\pubentry{TKDE 2022 ($Q1$, $A^*$)}{ Huynh Thanh Trung, Tong Van Vinh, Nguyen Thanh Tam, Jun Jo, Hongzhi Yin, Nguyen Quoc Viet Hung. \textbf{Learning Holistic Interactions in LBSNs with High-order, Dynamic, and Multi-role Contexts}. In TKDE 2022.}
\pubentry{TKDE 2022 ($Q1$, $A^*$)}{ Thanh Trung Huynh, Chi Thang Duong, Tam Thanh Nguyen, Vinh Van Tong, Abdul Sattar, Hongzhi Yin, Quoc Viet Hung Nguyen. \textbf{Network Alignment with Holistic Embeddings}. In TKDE 2022.}
\pubentry{KBS 2022 ($Q1$, IF 8.8)}{Thanh Tam Nguyen, Thanh Cong Phan, Minh Hieu Nguyen, Matthias Weidlich, Hongzhi Yin, Jun Jo, Quoc Viet Hung Nguyen. \textbf{Model-Agnostic and Diverse Explanations for Streaming Rumour Graphs}. In Knowledge-based Systems 2022.}
%\pubentry{ESWA 2022 ($Q1$)}{ Phan, Thanh Cong, Nguyen Duc Khang Quach, Thanh Tam Nguyen, Thanh Toan Nguyen, Jun Jo, Quoc Viet Hung Nguyen. \textbf{Real-time wildfire detection with semantic explanations}. In ESWA 2022.}
%\pubentry{PRL 2022}{ Thang, Duong Chi, Hoang Thanh Dat, Nguyen Thanh Tam, Jun Jo, Nguyen Quoc Viet Hung, Karl Aberer. \textbf{Nature vs. Nurture: Feature vs. Structure for Graph Neural Networks}. In Pattern Recognition Letters 2022.}
%\pubentry{MLWA 2022}{ Thanh Thi Nguyen, Mohamed Abdelrazek, Dung Tien Nguyen, Sunil Aryal, Duc Thanh Nguyen, Sandeep Reddy, Quoc Viet Hung Nguyen, Amin Khatami, Thanh Tam Nguyen et al. \textbf{Origin of novel coronavirus causing COVID-19: A computational biology study using artificial intelligence}. In MLWA 2022.}
\pubentry{TKDE 2021 ($Q1$, $A^*$)}{ Nguyen Thanh Tam, Huynh Thanh Trung, Hongzhi Yin, Tong Van Vinh, Darnbi Sakong, Bolong Zheng, Nguyen Quoc Viet Hung. \textbf{Entity Alignment for Knowledge Graphs with Multi-order Convolutional Networks}. In TKDE 2021.}
%\pubentry{Inf. Sci 2021 ($Q1$, $A$)}{ Nguyen Thanh Toan, Nguyen Thanh Tam, Bay Vo, Jun Jo, Quoc Viet Hung Nguyen. \textbf{JUDO: Just-in-time rumour detection in streaming social platforms}. In Information Sciences 2021.}
\pubentry{TKDE 2021 ($Q1$, $A^*$)}{ Duong Chi Thang, Nguyen Thanh Tam, Hongzhi Yin, Matthias Weidlich, Mai Thai Son, Karl Aberer, Nguyen Quoc Viet Hung. \textbf{Efficient and Effective Multi-Modal Queries through Heterogeneous Network Embedding}. In TKDE 2021.}
%\pubentry{ESWA 2021 ($Q1$)}{ Nguyen Thanh Toan, Nguyen Thanh Tam, Huynh Thanh Trung, Tong Van Vinh, Hoang Trung Dung, Nguyen Quoc Viet Hung, Quan Thanh Tho. \textbf{Structural representation learning for network alignment with self-supervised anchor links}. In ESWA 2021.}
%\pubentry{ASOC 2020 ($Q1$)}{ Nguyen Thanh Tam, Hoang Thanh Dat, Pham Minh Tam, Vu Tuyet Trinh, Nguyen Thanh Hung, Huynh Quyet Thang, Jun Jo. \textbf{Monitoring Agriculture Areas with Satellite Images and Deep Learning}. In Applied Soft Computing 2020.}
%\pubentry{IEEE ACCESS 2020 ($Q1$)}{ Phan Thanh Cong, Nguyen Thanh Tam, Hoang Thanh Dat, Nguyen Quoc Viet Hung, Jun Jo. \textbf{Multi-Scale Bushfire Detection From Multi-Modal Streams of Remote Sensing Data}. In IEEE ACCESS 2020.}
\pubentry{TIST 2019 ($Q1$, IF 10.5)}{ Nguyen Thanh Tam, Hongzhi Yin, Bolong Zheng, Nguyen Quoc Viet Hung, Bela Stantic. \textbf{Efficient User Guidance for Validating Participatory Sensing Data}. In ACM Transactions on Intelligent Systems and Technology 2019.}
%\pubentry{IS 2019 ($Q1$)}{ Nguyen Quoc Viet Hung, Matthias Weidlich, Nguyen Thanh Tam, Zoltan Miklos, Karl Aberer, Avigdor Gal, Bela Stantic. \textbf{Handling Probabilistic Integrity Constraints in Pay-as-you-go Reconciliation of Data Models}. In Information Systems Journal 2019. (IF 4.267)}
\pubentry{INFFUS  2019 ($Q1$, IF 18.6)}{ Thanh Tam Nguyen, Thanh Cong Phan, Quoc Viet Hung Nguyen, Karl Aberer, Bela Stantic. \textbf{Maximal Fusion of Facts on the Web with Credibility Guarantee}. In Information Fusion 2019.}
%\pubentry{IEEE Access 2018 ($Q1$)}{ Nguyen Thanh Toan, Phan Thanh Cong, Nguyen Thanh Tam, Nguyen Quoc Viet Hung, Bela Stantic. \textbf{Diversifying Group Recommendation}. In IEEE Access 2018. (IF 3.244)}
\pubentry{JVLDB 2017 ($A^*$)}{ Nguyen Quoc Viet Hung, Duong Chi Thang, Nguyen Thanh Tam, Matthias Weidlich, Karl Aberer, Hongzhi Yin, Xiaofang Zhou. \textbf{Answer Validation for Generic Crowdsourcing Tasks with Minimal Efforts}. In JVLDB 2017.}
\pubentry{JVLDB 2017 ($A^*$)}{ Nguyen Quoc Viet Hung, Duong Chi Thang, Nguyen Thanh Tam, Matthias Weidlich, Karl Aberer, Hongzhi Yin, Xiaofang Zhou. \textbf{Argument Discovery via Crowdsourcing}. In JVLDB 2017.}
\pubentry{TKDE 2017 ($A^*$, IF 9.235)}{ Nguyen Quoc Viet Hung, Huynh Huu Viet, Nguyen Thanh Tam, Matthias Weidlich, Hongzhi Yin, Xiaofang Zhou. \textbf{Computing Crowd Consensus with Partial Agreement}. In TKDE 2017.}
\normalsize

%\bigskip
\pubentry{}{}
\pubentry{}{{\textbf{\color{blue} Conference Papers}}}

%\small
\pubentry{ECML-PKDD 2024 ($A$)}{ Thanh Trung Huynh, Trong Bang Nguyen, Phi Le Nguyen, Thanh Tam Nguyen, Matthias Weidlich, Quoc Viet Hung Nguyen, Karl Aberer. \textbf{Fast-FedUL: A Training-Free Federated Unlearning with Provable Skew Resilience}. In European Conference on Machine Learning 2024.}
\pubentry{ICDE 2023 ($A^*$)}{ Thanh Tam Nguyen, Chi Thang Duong, Hongzhi Yin, Matthias Weidlich, Thai Son Mai, Karl Aberer, Quoc Viet Hung Nguyen. \textbf{Efficient and Effective Multi-Modal Queries through Heterogeneous Network Embedding}. In ICDE 2023.}
\pubentry{WSDM 2023 ($A^*$)}{ Thanh Trung Huynh, Minh Hieu Nguyen, Thanh Tam Nguyen, Phi Le Nguyen, Matthias Weidlich, Quoc Viet Hung Nguyen, Karl Aberer. \textbf{Efficient Integration of Multi-Order Dynamics and Internal Dynamics in Stock Movement Prediction}. In WSDM 2023.}
\pubentry{IJCNN 2023 ($A$)}{Zhao Ren, Thanh Tam Nguyen, Mehdi Mohammad Zahed, Wolfgang Nejdl. \textbf{Self-Explaining Neural Networks for Respiratory Sound Classification with Scale-Free Interpretability}. In IJCNN 2023.}
\pubentry{IJCNN 2023 ($A$)}{Thanh Toan Nguyen, Quang-Duc Nguyen, Zhao Ren, Jun Jo, Quoc Viet Hung Nguyen, Thanh Tam Nguyen. \textbf{10X Faster Subgraph Matching: Dual Matching Networks with Interleaved Diffusion Attention}. In IJCNN 2023.}
\pubentry{ICDE 2022 ($A^*$)}{ Thanh Cong Phan, Thanh Tam Nguyen, Matthias Weidlich, Honghzi Yin, Jun Jo, Quoc Viet Hung Nguyen. \textbf{exRumourLens: Auditable Rumour Detection with Multi-View Explanations}. In ICDE 2022.}
\pubentry{INTERSPEECH 2022 ($A$)}{ Yi Chang, Zhao Ren, Thanh Tam Nguyen, Wolfgang Nejdl, Bjorn W. Schuller. \textbf{Example-based Explanations with Adversarial Attacks for Respiratory Sound Analysis}. In INTERSPEECH 2022.}
%\pubentry{ICASSP 2022}{ Zhao Ren, Thanh Tam Nguyen, Wolfgang Nejdl. \textbf{Prototype Learning for Interpretable Respiratory Sound Analysis}. In ICASSP 2022.}
\pubentry{SIGMOD 2021 ($A^*$)}{ Bo Zhao, Han van der Aa, Thanh Tam Nguyen, Quoc Viet Hung Nguyen, Matthias Weidlich. \textbf{EIRES: Efficient Integration of Remote Data in Event Stream Processing}. In SIGMOD 2021.}
%\pubentry{ADMA 2021}{ Chau Xuan Truong Du, Nguyen Thanh Tam, Jun Jo, Nguyen Quoc Viet Hung. \textbf{Are Rumors Always False?: Understanding Rumors Across Domains, Queries, and Ratings}. In ADMA 2021.}
\pubentry{SIGIR 2020 ($A^*$)}{ Thanh Tam Nguyen, Matthias Weidlich, Hongzhi Yin, Bolong Zheng, Quang Huy Nguyen and Quoc Viet Hung Nguyen. \textbf{FactCatch: Incremental Pay-as-You-Go Fact Checking with Minimal User Effort}. In SIGIR 2020.}
\pubentry{ICDE 2020 ($A^*$)}{ Thanh Trung Huynh, Van Vinh Tong, Thanh Tam Nguyen, Hongzhi Yin, Matthias Weidlich, Quoc Viet Hung Nguyen. \textbf{Adaptive Network Alignment with Unsupervised and Multi-order Convolutional Networks}. In ICDE 2020.}
\pubentry{VLDB 2019 ($A^*$)}{ Nguyen Thanh Tam, Matthias Weidlich, Hongzhi Yin, Bolong Zheng, Nguyen Quoc Viet Hung, Bela Stantic. \textbf{User Guidance for Efficient Fact Checking}. In VLDB 2019.}
\pubentry{VLDB 2019 ($A^*$)}{ Nguyen Thanh Tam, Matthias Weidlich, Bolong Zheng, Hongzhi Yin, Nguyen Quoc Viet Hung, Bela Stantic. \textbf{From Anomaly Detection to Rumour Detection using Data Streams of Social Platforms}. In VLDB 2019.}
\pubentry{ICDE 2018 ($A^*$)}{ Nguyen Quoc Viet Hung, Kai Zheng, Matthias Weidlich, Bolong Zheng, Hongzhi Yin, Nguyen Thanh Tam, Bela Stantic. \textbf{What-if Analysis with Conflicting Goals: Recommending Data Ranges for Exploration}. In ICDE 2018.}
\pubentry{IJCAI 2017 ($A^*$)}{ Nguyen Thanh Tam, Matthias Weidlich, Duong Chi Thang, Hongzhi Yin, Nguyen Quoc Viet Hung. \textbf{Retaining data from streams of social platforms with minimal regret}. In IJCAI 2017.}
\pubentry{ICDE 2015 ($A^*$)}{ Nguyen Quoc Viet Hung, Nguyen Thanh Tam, Chau Vinh Tuan, Tri Kurniawan Wijaya, Zoltan Miklos, Karl Aberer, Avigdor Gal and Matthias Weidlich. \textbf{SMART: A tool for analyzing and reconciling schema matching networks}. In ICDE 2015.}
\pubentry{ICDE 2015 ($A^*$)}{ Nguyen Thanh Tam, Nguyen Quoc Viet Hung, Matthias Weidlich and Karl Aberer. \textbf{Result Selection and Summarization for Web Table Search}. In ICDE 2015.}
%\pubentry{DEXA 2015 ($A$)}{Duong Chi Thang, Nguyen Thanh Tam, Nguyen Quoc Viet Hung and Karl Aberer. \textbf{An Evaluation of Diversification Techniques}. In DEXA 2015.}
%\pubentry{DASFAA 2015 ($A$)} {Nguyen Quoc Viet Hung, Do Son Thanh, Nguyen Thanh Tam, Karl Aberer. \textbf{Tag-based Paper Retrieval: Minimizing User Effort with Diversity Awareness}. In DASFAA 2015.}
%\pubentry{DASFAA 2014 ($A$)}{ Nguyen Quoc Viet Hung, Do Son Thanh, Nguyen Thanh Tam, Karl Aberer. \textbf{Privacy-Preserving Schema Reuse}. In DASFAA 2014.}
\pubentry{ICDE 2014 ($A^*$)}{ Nguyen Quoc Viet Hung, Nguyen Thanh Tam, Zoltan Miklos, Karl Aberer, Avigdor Gal and Matthias Weidlich, \textbf{Pay-as-you-go Reconciliation in Schema Matching Networks}. In ICDE 2014.}
\pubentry{WISE 2013 ($A$)}{ Nguyen Quoc Viet Hung, Nguyen Thanh Tam, Lam Ngoc Tran, Karl Aberer, \textbf{An Evaluation of Aggregation Techniques in Crowdsourcing}, In WISE 2013.}
\pubentry{SIGIR 2013 ($A^*$)}{ Nguyen Quoc Viet Hung, Nguyen Thanh Tam, Lam Ngoc Tran, Karl Aberer, \textbf{A Benchmark for Aggregation Techniques in Crowdsourcing}, In SIGIR 2013.}
\pubentry{DASFAA 2013 ($A$)}{ Nguyen Quoc Viet Hung, Nguyen Thanh Tam, Zoltan Miklos, Karl Aberer, \textbf{On Leveraging Crowdsourcing Techniques for Schema Matching Networks} , In DASFAA 2013 (Best Student Paper Award)}
\end{pub}