% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Scholarships and additional info

\sectionTitle{Student Mentoring}{\faMortarBoard}

\begin{scholarship}
\scholarshipentry{PhD theses}
{Trinh Pham, \textbf{``Enhancing Recommender Systems with Privacy-Driven Personalized Explanations''}, Griffith University, Australia (2025-2028, Principal Supervisor).}
\scholarshipentry{}
{Minh Tam Pham, \textbf{``Efficient and Effective Deepfake Detection System''}, Griffith University, Australia (2024-2027, Principal Supervisor).}
\scholarshipentry{}
{Thanh Dat Hoang, \textbf{``Conversational Question Answering System with High Precision and Reliability''}, Griffith University, Australia (2024-2027, Principal Supervisor).}
\scholarshipentry{}
{Bowen Yang, \textbf{``Maket volatility calibration: A neural network approach''}, Griffith University, Australia (2026-2029).}
\scholarshipentry{}
{Nam Trung Nguyen, \textbf{``AI and Human Security in Developing Countries: Legal Challenges and Vietnam's Response''}, Griffith University, Australia (2026-2029).}
\scholarshipentry{}
{Viet Hung Vu, \textbf{``A Smart Digital Twin for Bushfire Monitoring and Detection System''}, Griffith University, Australia (2025-2028).}
\scholarshipentry{}
{Chaoqun Yang, \textbf{``Elastic Federated Learning with Fairness and Privacy Guarantees''}, Griffith University, Australia (2023-2026).}
\scholarshipentry{}{Darnbi Sakong, \textbf{``Graph Representation Learning: Advanced Applications and Methods''}, Griffith University, Australia (2021-2024).}
\scholarshipentry{}{Cailen Robertson, \textbf{``Distributed processing in IoT Architectures for efficient deep learning''}, Griffith University, Australia (2019-2022). \textbf{(Best Student Paper Award RITA 2022)}}
	\scholarshipentry{}
					{Thanh Cong Phan,  \textbf{``Explanation as First-Class Citizen: Methods and Applications''}, Griffith University, Australia (2019-2022). \textbf{(Best Paper Award RITA 2019)}}
	\scholarshipentry{}
					{Thanh Toan Nguyen, \textbf{“Scalable Subgraph Mining: Methods and Applications”}, Griffith University, Australia (2019-2023)}
	\scholarshipentry{}
					{Wei Zhang, \textbf{"Machine Unlearning in Audio Applications"}, Leibniz University Hannover, Germany (2020-2024). (Co-supervision with Prof. Wolfgang Nejdl and Dr. Zhao Ren)}
	\scholarshipentry{Master theses}
					{Ken Quach, \textbf{"Traffic Demand Prediction with Graph Neural Networks"}, Griffith University, Australia (2022, Honour Degree)}
	\scholarshipentry{}
					{Guanqiao Sui, \textbf{"Skeptical Learning for Sound Classification"}, Leibniz University Hannover, Germany (2022)}
	\scholarshipentry{}
					{Mohammad Mehdi Zahed, \textbf{"Interpretable Machine Learning for Sound Classification"}, Leibniz University Hannover, Germany (2021)}
	\scholarshipentry{}
					{Cyril van Schreven, \textbf{``Deepbot: Build a poker bot using Big Data and Deep Learning techniques''}, EPFL, Switzerland \textbf{(Best Research Master Thesis)}}
	\scholarshipentry{}
					{Matthieu Gaston Michel Albert Devaux, \textbf{"Deep Learning for Music: Similarity Search and Beyond"}, EPFL}
	\scholarshipentry{}
					{Claudio Leao Loureiro, \textbf{``Artificial Intelligence for Industrial Applications''}, ABB, Switzerland \textbf{(Best Industry Master Thesis)}}
\scholarshipentry{Honour theses}
					{Baraa Ragab Tbab, \textbf{"Debunking Medical Misinformation - Rootcauses, Benchmarks, and Explanations"}, Leibniz University Hannover, Germany (2021)}	
	\scholarshipentry{}
					{Orcun Gumus, \textbf{``DeepForecast: Joint Fusion Learning of Multiple Time Series Prediction''}, EPFL}
	\scholarshipentry{}
					{Davide Di Dio, \textbf{``DeepSuccess: Predict the Success of Tech Startups''}, EPFL}
\end{scholarship}

%\sectionTitle{Teaching and Mentoring}{\faMortarBoard}

%\begin{experiences}
%  \experience
%    {Master theses}   {Architecte logiciel | Développeur/Concepteur Senior JEE}{EPFL}{Switzerland}
%    {Décembre 2015} {
%                      \begin{itemize}
%                        \item Reconstruction de la plateforme d'intégration                        
%                        \item Migration de l'ensemble des projets Java sous Maven                    
%                        \item Evolutions et corrections des bugs du framework de développement interne                
%                        \item Veille technologique                                                                    
%                      \end{itemize}
%                    }
%                    {Apache Tomcat, IntelliJ Idea, Eclipse, Maven, Spring Boot, Jenkins, Nexus}
%  \emptySeparator
%\end{experiences}